### 2023-10-25 intro.tex
Remove most usages of "local type inference"

The user can interactively explore possible error localizations by hovering over a partially consistent suggestion, which (temporarily) fills the type hole and thus returns the localization decision to the local inference system.
Here, each choice causes a different set of two uses of \li{x} to be marked, e.g. the first and third use for \li{Int -> Int} (shown above). Until the choice is finalized, the type hole continues to operate gradually.
\cref{sec:thi} describes this distinctively neutral approach to blending local and constraint-based type inference in Hazel, where local inference is used to systematically mark erroneous expressions in the program and constraint-based inference (using entirely standard algorithms, which we do not repeat in this paper) is used exclusively to locate unfillable holes.

>>>>

The user can interactively explore possible error localizations by hovering over a partially consistent suggestion, which (temporarily) fills the type hole and thus returns the localization decision to the bidirectional type system.
Here, each choice causes a different set of two uses of \li{x} to be marked, e.g. the first and third use for \li{Int -> Int} (shown above). Until the choice is finalized, the type hole continues to operate gradually.
\cref{sec:thi} describes this distinctively neutral approach to blending local and constraint-based
type inference in Hazel, where bidirectional typing is used to systematically mark erroneous expressions in the program and constraint-based inference (using entirely standard algorithms, which we do not repeat in this paper) is used exclusively to locate unfillable holes.

### 2023-10-25 related.tex
Remove most usages of "local type inference"

A more neutral alternative is to derive a set of terms that contribute to an error, an approach known as type error slicing \cite{DBLP:conf/esop/HaackW03,DBLP:journals/tosem/TipD01,DBLP:conf/sfp/Schilling11}. This creates a large amount of information for the programmer to consume. Our approach is to instead simply report the constraint inconsistencies on a hole in the program and allow for the programmer to interactively refine their intent, so only the local inference system is responsible for identifying particular erroneous expressions. We do not make particular usability claims about the interactive affordances related to type hole inference in this paper, but rather simply claim a novel neutral point in the overall design space that uniquely combines local and global approaches.

@@

The underlying unification algorithm is essentially standard--the novelty is in how the unification results are used and how failures are handled, rather than in the inference itself. In particular, we base our approach on the system described by \cite{GradualInfer}, because it also identifies type inference variables with the unknown type from gradual typing and the union find data structure is useful for computing possible type sets. \citet{garcia:2015} similarly present a static implicitly typed language, where users opt into dynamism by annotating an expression with the gradual type "?", and an associated type inference algorithm and accompanying metatheory. By contrast, the Hazelnut type system assigns gradual types to programs that would ordinarily not type-check in a non-gradual system by wrapping them in expression holes. The type inference algorithm presented in \citet{garcia:2015} also does not specify what to do if the constraint set cannot be solved. If a single static type cannot be determined for an expression, its type is simply undefined, whereas our approach provides a list of suggestions derived from any conflicting constraints if a single substitution cannot be determined. As our focus is on failure cases and partially consistent suggestions, the metatheory in this prior work is less relevant in guiding the design of the type hole inference system.

>>>>

A more neutral alternative is to derive a set of terms that contribute to an error, an approach known as type error slicing \cite{DBLP:conf/esop/HaackW03,DBLP:journals/tosem/TipD01,DBLP:conf/sfp/Schilling11}. This creates a large amount of information for the programmer to consume. Our approach is to instead simply report the constraint inconsistencies on a hole in the program and allow for the programmer to interactively refine their intent, so only the bidirectional type system is responsible for identifying particular erroneous expressions. We do not make particular usability claims about the interactive affordances related to type hole inference in this paper, but rather simply claim a novel neutral point in the overall design space that uniquely combines local and global approaches.

@@

The underlying unification algorithm is essentially standard---the novelty is in how the unification results are used and how failures are handled, rather than in the inference itself. In particular, we base our approach on the system described by \citet{GradualInfer}, because it also identifies type inference variables with the unknown type from gradual typing and the union find data structure is useful for computing possible type sets. \citet{garcia:2015} similarly present a static implicitly typed language, where users opt into dynamism by annotating an expression with the gradual type "?", and an associated type inference algorithm and accompanying metatheory. By contrast, the Hazelnut type system assigns gradual types to programs that would ordinarily not type-check in a non-gradual system by wrapping them in expression holes. The type inference algorithm presented in \citet{garcia:2015} also does not specify what to do if the constraint set cannot be solved. If a single static type cannot be determined for an expression, its type is simply undefined, whereas our approach provides a list of suggestions derived from any conflicting constraints if a single substitution cannot be determined. As our focus is on failure cases and partially consistent suggestions, the metatheory in this prior work is less relevant in guiding the design of the type hole inference system.
